Plant species traits and growth rates: meta-analysis shows correlations change with plant size as predicted

### 2015-07-16 MS.tex
Add Fig11 (model growth and measurment)

Across the 112 article used in our meta-analyses, plants were categorized into four stages according to the expertise and the apprciation of the authors (i.e.seedling, juvenile, sapling, adult). 
While by compiling data across multiple studies there is a risk of assigning plants of similar size to different categories, the thershold size is standardized for a plant stage across the 112 studies ().

@@

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA6.pdf}
\caption{\textbf{Effect size (+ 95\%CI) of plant stage on the
correlations between growth rate and five functional traits \textcolor{red}{across and between species}} Effects size are calculated for a) Specific leaf area (SLA), b) Wood density (WD), c) Net assimilation rate (NARarea), d) Seed mass, e) Asymptotic height (Hmax) and f) Assimilation rate of CO2 (Aarea). Effect size is a standardized measure of the magnitude of the relationship between a particular stage and the correlation coefficient z (Fisher's z-transformed). Effects are significant if confidence intervals (+CI95\%) do not overlap with zero. LRT: likelihood Ratio Test compared the fit between null model and stage model, both models are fitted by Maximum Likelihood. Black point: ideal data (at interspecific level and under unstressed conditions), grey points: raw data (at both intra and interspecific level and under both stress and unstressed conditions). 'n' indicate the number of independent comparisons for each effect.
}
\label{FigA6}
\end{figure}

>>>>

Across the 112 article used in our meta-analyses, plants were categorized into four stages according to the expertise and the appreciation of the authors (i.e.seedling, juvenile, sapling, adult). While by compiling data across multiple studies there is a risk of assigning plants of similar size to different categories, the threshold in size/age used by the authors to defined a plant stage are quite standardized across the 112 studies (Fig. \ref{FigA1}).

@@

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA6.pdf}
\caption{\textbf{Effect size (+ 95\%CI) of plant stage on the
correlations between growth rate and five functional traits \textcolor{red}{across and between species}} Effects size are calculated for a) Specific leaf area (SLA), b) Wood density (WD), c) Net assimilation rate (NARarea), d) Seed mass, e) Asymptotic height (Hmax) and f) Assimilation rate of CO2 (Aarea). Effect size is a standardized measure of the magnitude of the relationship between a particular stage and the correlation coefficient z (Fisher's z-transformed). Effects are significant if confidence intervals (+CI95\%) do not overlap with zero. LRT: likelihood Ratio Test compared the fit between null model and stage model, both models are fitted by Maximum Likelihood. \textcolor{red}{Shown here are the "raw dataset" (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions)}. 'n' indicate the number of independent comparisons for each effect.
}
\label{FigA6}
\end{figure}
